\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-23 chapters/1_intro.tex
Update Fig 1

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.85\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of three different agglomerative algorithms included in our proposed generalized clustering framework. The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). The final clustering / instance segmentation is shown in 3c, overlaid with the raw image. In 3a, we also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.95\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of three different agglomerative algorithms included in our proposed generalized clustering framework. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). In 3c, we also illustrate some iterations of the algorithms on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}
